Finding a closest point in a lattice of Voronoi's first kind

### 2014-01-11 paper.tex
minor

The root lattices $A_n$ and their dual lattices $A_n^*$ are classical examples of lattices of Voronoi's first kind~\cite{SPLAG}.  The construction of an `arbitrary' lattice of Voronoi's first kind appears nontrivial.  One approach would be to construct the matrix $Q = B^\prime B$ containing the Selling parameters $q_{ij}$.  The matrix $Q$ requires to have nonegative off diagonal entries and to be positive semidefinite with null space containing the vector $\onebf$ of all ones.  The explicit construction of such matrices is an interesting question for future research.  A related question is to determine, in some sense, how `large' the set of matrices satisfying these criteria is.  This would shed some light on how `large' the set of lattices of Voronoi's first kind is.

>>>>

The root lattices $A_n$ and their dual lattices $A_n^*$ are classical examples of lattices of Voronoi's first kind~\cite{SPLAG}.  The construction of an `arbitrary' lattice of Voronoi's first kind appears nontrivial.  One approach would be to construct the matrix $Q = B^\prime B$ containing the Selling parameters $q_{ij}$.  The matrix $Q$ requires to have nonpositive off diagonal entries and to be positive semidefinite with null space containing the vector $\onebf$ of all ones.  The explicit construction of such matrices is an interesting question for future research.  A related question is to determine, in some sense, how `large' the set of matrices satisfying these criteria is.  This would shed some light on how `large' the set of lattices of Voronoi's first kind is.
